Training an Agent on Brainwaves

### 2019-09-26 ErrP.tex
Subo una versión más depurada del paper

\begin{figure}[h]
        \centering
        \includegraphics[scale=0.4]{Images/Average_steps/alex.png} 
        \caption{Average steps using Q-table trained with the results of subject 1}
        \label{fig:avg_steps_1}
\end{figure}

\begin{figure}[h]
        \centering
        \includegraphics[scale=0.4]{Images/Average_steps/gonza.png} 
        \caption{Average steps using Q-table trained with the results of subject 2}
        \label{fig:avg_steps_2}
\end{figure}

\begin{figure}[h]
        \centering
        \includegraphics[scale=0.4]{Images/Average_steps/jose.png} 
        \caption{Average steps using Q-table trained with the results of subject 3}
        \label{fig:avg_steps_3}
\end{figure}

\begin{figure}[h]
        \centering
        \includegraphics[scale=0.4]{Images/Average_steps/juan.png} 
        \caption{Average steps using Q-table trained with the results of subject 4}
        \label{fig:avg_steps_4}
\end{figure}

\begin{figure}[h]
        \centering
        \includegraphics[scale=0.4]{Images/Average_steps/manu.png} 
        \caption{Average steps using Q-table trained with the results of subject 5}
        \label{fig:avg_steps_5}
\end{figure}

\begin{figure}[h]
        \centering
        \includegraphics[scale=0.4]{Images/Average_steps/marta.png} 
        \caption{Average steps using Q-table trained with the results of subject 6}
        \label{fig:avg_steps_6}
\end{figure}

\begin{figure}[h]
        \centering
        \includegraphics[scale=0.4]{Images/Average_steps/nati.png} 
        \caption{Average steps using Q-table trained with the results of subject 7}
        \label{fig:avg_steps_7}
\end{figure}

\begin{figure}[h]
        \centering
        \includegraphics[scale=0.4]{Images/Average_steps/santiago.png} 
        \caption{Average steps using Q-table trained with the results of subject 8}
        \label{fig:avg_steps_8}
\end{figure}

>>>>

\begin{figure}[h!]
\begin{subfigure}{0.5\textwidth}
\includegraphics[scale=0.2]{Images/Average_steps/alex.png}
\includegraphics[scale=0.2]{Images/Average_steps/gonza.png}
\includegraphics[scale=0.2]{Images/Average_steps/jose.png}
 \includegraphics[scale=0.2]{Images/Average_steps/juan.png} 
\caption{Initial state of the grid.}
\label{fig:subim1}
\end{subfigure}
\begin{subfigure}{0.5\textwidth}
 \includegraphics[scale=0.2]{Images/Average_steps/manu.png} 
  \includegraphics[scale=0.2]{Images/Average_steps/marta.png} 
  \includegraphics[scale=0.2]{Images/Average_steps/nati.png} 
  \includegraphics[scale=0.2]{Images/Average_steps/santiago.png} 
\caption{Final state of the grid.}
\label{fig:subim2}
\end{subfigure}
\caption{Grid system representation used in cognitive experience.}
\label{fig:game_representation}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[scale=0.4]{Images/Average_steps/noise.png}
\caption{Average steps using Q-Table trained with noise.}
\label{fig:avg_steps_noise}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[scale=0.4]{Images/algorithm_calibration/Total_calib.png}
    \caption{Score Obtained With The Optimal Calibration Per Algorithm Per Subject}
    \label{diag:algorithm_calibration:subject_calib}
\end{figure}
